% \documentclass[draft]{book}
\documentclass[draft]{book}

\usepackage{graphicx}

\usepackage{epstopdf}
\usepackage{epsfig}

\usepackage{float}
\usepackage{amssymb,amsmath}
\newcommand{\bm}[1]{\boldsymbol{#1}}

\usepackage[makeroom]{cancel} %for cancel out in eq.

\usepackage{multirow}
\usepackage{fullpage}
\usepackage{appendix}
\usepackage{setspace}

\usepackage[bf, small, center]{caption}
\setlength{\belowcaptionskip}{10pt}

\usepackage{longtable}

\usepackage{geometry}
\geometry{
%  top=1.0in,  
%  inner=1.5in,
%  outer=1.5in,
  bottom=1.2in,
%  headheight=3ex, 
  headsep=3ex,         
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[LO, RE]{\rightmark}
\fancyhead[LE, RO]{\thepage}
\fancyfoot[]{}
%\renewcommand{\headrulewidth}{0.3pt}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}



\usepackage[phd]{thesisfrontmatter}

% *** NOTE WHICH PROGRAM GENERATED IMAGES OR WHICH POWER POINT THEY ARE FROM
%compare methodology with script for final process
%how much detail in methodology?
%some sort of processing flowchart?
%how much do we care about processing?

\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent


\usepackage{mathtools}


\usepackage{color}
\usepackage{soul}



\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\let\stdsection\chapter  
\renewcommand\chapter{\newpage\stdsection}  

%%%%%%%%%%% for Appendix
\makeatletter
\newcommand\appendix@section[1]{%
  \refstepcounter{section}%
  \orig@section*{Appendix \@Alph\c@section: #1}%
  \addcontentsline{toc}{section}{Appendix \@Alph\c@section: #1}%
}
\let\orig@section\section
\g@addto@macro\appendix{\let\section\appendix@section}
\makeatother

% Added 12-03-13 ----------------------------------------
\usepackage{imakeidx} % to create index
\indexsetup{othercode=\small}
\makeindex[program=makeindex,columns=2,intoc=true,options={-s MyIndex.ist}]
% -------------------------------------------------------
%%%%%%%%%%%%%%

\usepackage{hyperref}
\hypersetup{
    % bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in AcrobatÕs bookmarks
    pdftoolbar=true,        % show AcrobatÕs toolbar?
    pdfmenubar=true,        % show AcrobatÕs menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={L8's potential for water constituents retrieval },    % title
    pdfauthor={Javier Concha},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=blue,          % color of internal links
    citecolor=cyan,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

\usepackage[all]{hypcap} % to see figure with hyper ref

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

% Added 11-12-13 ----------------------------------------

\usepackage{titlesec} % For the spacing after and before chapter title

\titleformat{\chapter}[display]
    {\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{10pt}{\Huge}
\titlespacing*{\chapter}{0pt}{40pt}{20pt}

\titlespacing*{\section}{0ex}{2.5ex}{2ex}
\titlespacing*{\subsection}{0ex}{1.5ex}{1ex}

\usepackage{indentfirst}
\setlength{\parindent}{20pt}
\doublespacing

% Added 11-17-13 ----------------------------------------
% Select what to do with todonotes: 
% \usepackage[disable]{todonotes} % notes not showed
\usepackage[draft]{todonotes}   % notes showed

\setlength{\marginparwidth}{3.7cm}

% Added 11-15-13 ----------------------------------------
\includeonly{Introduction,Objectives,Background_and_Theory,Methodology,Results,Summary,Appendix} 
% \includeonly{Methodology} 
% \includeonly{Introduction,Objectives,Background_and_Theory,Methodology,Results} 
\usepackage{tikz} % for flow charts
  \usetikzlibrary{shapes,arrows,positioning,shadows,calc}

\begin{filecontents*}{linereg.data}
#x y
0 4
10 24
\end{filecontents*} 

\begin{filecontents*}{linereg2.data}
#x y
2 8
8 20
\end{filecontents*}
 
\usepackage{colortbl}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}

\listfiles

\setlength{\headheight}{15pt} % to avoid "Package Fancyhdr Warning: \headheight is too small (0.0pt): Make it at least 12.0pt."

% Added 02-18-14 ----------------------------------------
% \setlength{\abovecaptionskip}{-2ex}
% \setlength{\belowcaptionskip}{-4ex} % space after caption
%******************************************************************************************************


% Added 08-10-14 
\usepackage{enumitem}

% Added 07-28-15 
\usepackage[percent]{overpic}
\usepackage{morefloats} % for the error "Too many unprocessed floats"

%******************************************************************************************************
%******************************************************************************************************
%******************************************************************************************************
\begin{document}

\degreetitle{The Use of Landsat 8 for Monitoring of Fresh and Coastal Water}
\degreeauthor{Javier A. Concha}
\degreedate{November 10, 2015}
% \degreedate{\today{}}
\prevdegreeA{B.S. Electronics Engineering, Universidad de Concepci\'on, Chile, 2008}
\prevdegreeB{M.S. Imaging Science, Rochester Institute of Technology, NY, USA, 2012}
\advisor{Dr. John R. Schott}
\memberA{Dr. Anthony Vodacek}
\memberB{Dr. Charles Bachmann}
\memberC{Dr. Christy Tyler}
% \memberD{Dr. Christy Tyler}

\makedeclaration


\makePHDproposalapproval
\makecopyright


% \maketitle

\pagenumbering{roman}

% \chapter*{Abstract}
% \addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}
\setlength{\parindent}{20pt}
% 300 Words max.
% Background/motivation/context
The most interaction between humankind and water occurs in coastal and inland waters (Case 2 waters) at a scale of tens or hundred of meters, but there is not yet an ocean color product at this spatial scale. % taken from SPIE SD paper
% 
Landsat 8 is a promising candidate to address the remote sensing of these kinds of waters due to its improved signal-to-noise ratio (SNR), spectral resolution, 12-bit quantization, and high spatial resolution. 
%
Landsat 8 is the next generation of Landsat satellite and continues more than 40 years of uninterrupted imaging acquisition, playing a critical role in monitoring, understanding and managing natural resources such as water.

Landsat 8 has the potential to dramatically improve our ability to simultaneously retrieve the three primary coloring agents, chlorophyll-{\it a}, colored dissolved organic material (CDOM) and suspended material (SM) from water bodies. This work presents an approach to obtain these coloring agents in coastal and fresh waters.

% Aim/objectives(s)/problem statement
In the Case 2 water problem, the sensor-reaching signal due to water is very small when compared to the signal due to the atmospheric effects. Therefore, adequate atmospheric correction becomes an important first step to accurately retrieving water parameters. 

Standard atmospheric correction algorithms developed for heritage ocean color instruments (e.g. MODIS, SeaWiFS) require a sufficient SNR in two bands where the water-leaving signal is negligible, which is not always possible, particularly for Landsat 8's bands.

As a first approach, a model based empirical line method (MoB-ELM) atmospheric correction method converts sensor-reaching radiance to water leaving reflectance. This model employs pseudo invariant feature (PIF) pixels extracted from Landsat images along with an in water radiative transfer model (HydroLight) to obtain the field spectra. Further atmospheric compensation technique based in algorithms currently used in Ocean Color sensors will be investigated.

% added from RS of Env. paper
New approaches need to be considered to solve the current high demand for color producing agent (CPA) retrievals over inland and coastal waters (Case 2 waters). 
%
Standard retrieval algorithms are known to fail over highly turbid Case 2 waters because they were developed specifically for the open ocean (Case 1 waters). 
 
%Methods
A look-up-table (LUT) and spectrum-matching methodology was implemented to simultaneously retrieve CPAs, taking advantage of Landsat 8's new features. 
%
A LUT of spectral remote-sensing reflectances ($R_{rs}$) with different concentration of CPAs was produced using the in-water radiative transfer model Hydrolight. 
%Results
The retrieval algorithm was applied over two Landsat 8 scenes and shows a root mean squared error (RMSE) as a percentage of range of about $10\%$ for Chlorophyll-{\it a} and total suspended solid (TSS), and about $5\%$ for colored dissolved organic matter (CDOM) when compared with ground-truth data. The CPA concentration maps exhibit expected trends of low concentrations in clear water and higher concentrations in turbid water.
%Conclusions

These results demonstrate that the developed algorithm allows the simultaneous mapping of concentration of all CPAs in Case 2 waters and over areas where the standard algorithms are not available due to spatial resolution.
%
Therefore, this study shows that the Landsat 8 satellite can be utilized over Case 2 waters as long as a careful atmospheric correction is applied. 

Collections of water samples when the satellite passes over the Rochester area are planned for summer 2013, 2014 and 2015. Concentration and inherent optical properties (IOPs) measurement will help to validate the methods.

% Background/motivation/context
% Aim/objectives(s)/problem statement
% Approach/method(s)/procedure(s)/materials
% Results
% Conclusion(s)/implications

\end{abstract}

% \chapter*{Acknowledgements}
% %*****************************************************************************************************
\begin{acknowledgements}
\setlength{\parindent}{20pt}
% To my parents, Osvaldo Concha and Nelly Sepulveda, sister Loretto Concha and brother Alvaro Concha. USGS. Monroe County Environment: Scott, Providencia and Gary. Nina and Rolo. Dr. Christy Taylor. Paul. Aaron Gerace. Alan Wiedmman. Ocean Color community: Emmanuel Boss and attendants of the 2013 Ocean color and instrumentation summer course at the Darling Marine Center. Fulbright commission. My advisor Dr. John Schott. Amanda and Cindy. Classmates: Aly, Bikash, Viraj, Madurima, Peter Sun. Professor Dr. John Kerekes. Collection help: Harold Valdivia. My dear friends: Juan Saldana, Kader, Patrick, Sarada, Susan, Melisa, Sasha, Jeremy. The people at Crossfit Rochester: Joe, Andrew. The Latin Rhythm Dance Club at RIT. My best support here Aixa de Jesus. My adopted Chilean family and dancers in Rochester: Marcia, Rosa and Doña Rosita, Raul, Willy and Marisol, Harold and Nancy. My Chilean friends in U. of R. Felipe, Maria Eugenia, Emilio, Brenda and Pauly. Kimberley Thoms.
\end{acknowledgements}
%*****************************************************************************************************

\begin{dedication}

Dedicated to

Mis amados viejitos, Osvaldo Concha Silva and Nelly del Carmen Sep\'ulveda Reyes...
\end{dedication}

\tableofcontents

\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}

\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

% \input{Introduction.tex}
\include{Introduction}
\include{Objectives}
\include{Background_and_Theory}
\include{Methodology}
\include{Results}
\include{Summary}
\include{Appendix}

\listoftodos

%\bibliographystyle{ieeetr}
%\bibliographystyle{unsrtnat}
\bibliographystyle{apalike}

\bibliography{/Users/javier/Desktop/Javier/PHD_RIT/Latex/javier_bib}

\printindex

\end{document}  